### 2024-05-18 fantasy-football.qmd
20240518 - headings
20240518 - typo

As noted in the [Introduction](intro.qmd), fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.^[Fantasy leagues are also available [baseball](https://en.wikipedia.org/wiki/Fantasy_baseball), [basketball](https://en.wikipedia.org/wiki/Fantasy_basketball), and many other sports.]
The participants are in charge of managing and making strategic decisions for their imaginary team to have the best possible team that will score the most points.
Thus, the participants are called "managers".
Managers make decisions such as selecting which players to draft, selecting which players to play (i.e., "start") on a weekly basis, identifying players to pick up from the remaining pool of available players (i.e., waiver wire), and making trades with other teams.
Fantasy football relies heavily on prediction—trying to predict which players will perform best and selecting them accordingly.

@@

@@

Here are common scoring settings for fantasy leagues:

@@

@@

<u>Team Defense/Special Teams:</u>

@@

<u>Individual Defensive Players:</u>

@@

Common scoring abbreviations:

>>>>

As noted in the [Introduction](intro.qmd), fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.^[Fantasy leagues are also available for [baseball](https://en.wikipedia.org/wiki/Fantasy_baseball), [basketball](https://en.wikipedia.org/wiki/Fantasy_basketball), and many other sports.]
The participants are in charge of managing and making strategic decisions for their imaginary team to have the best possible team that will score the most points.
Thus, the participants are called "managers".
Managers make decisions such as selecting which players to draft, selecting which players to play (i.e., "start") on a weekly basis, identifying players to pick up from the remaining pool of available players (i.e., waiver wire), and making trades with other teams.
Fantasy football relies heavily on prediction—trying to predict which players will perform best and selecting them accordingly.

@@

#### Scoring Overview {#sec-scoringOverview}

@@

Below are common scoring settings for fantasy leagues.

#### Offensive Players {#sec-scoringOffense}

@@

#### Kickers {#sec-scoringKickers}

@@

#### Team Defense/Special Teams {#sec-scoringDST}

@@

#### Individual Defensive Players {#sec-scoringIDP}

@@

#### Common Scoring Abbreviations {#sec-scoringAbbreviations}
